\chapter{Tasks Performed}

\section{Summary of Tasks Performed}

During the internship, I contributed to the development and enhancement of the \textbf{CBCC-PWA (Co-Branded Credit Card Progressive Web App)}, a mobile-first financial platform designed for credit card customers. I worked extensively with React, Redux, TypeScript, REST APIs, and Progressive Web Application (PWA) architecture to develop scalable and reusable frontend components for modules such as Card Management, EMI Management, Customer Care, and Offer Management. I also improved application responsiveness and user experience by implementing modern UI enhancements including CSS variables, theme tokens, glassmorphism effects, and micro-animations, which helped create a more consistent and visually optimized interface across devices.

\section{Problem Statement/Goal}

The primary objective of the assigned work was to improve the scalability, usability, and maintainability of the CBCC-PWA platform while ensuring secure and seamless customer interactions. The project addressed challenges related to modernizing the existing user interface, implementing safe workflows for updating live financial offers, and enabling secure API communication using OTP/MPIN-based authentication mechanisms. Another key goal was to support dynamic feature control based on banking restrictions and customer account status, thereby improving operational reliability and user experience.

\section{Implementation Details}

The frontend application was implemented using a reusable component-based architecture with React, Redux, and TypeScript, allowing easier maintenance and faster feature development. I contributed to secure API integration by implementing centralized authentication handling that supported request validation, OTP/MPIN verification, session management, and secure state synchronization using Redux. A significant part of the internship involved contributing to the \textbf{Hyperface Live Offer Versioning Workflow}, where I helped implement and document mechanisms such as automatic offer cloning, field-level change detection, maker-checker approval flow, and controlled publishing strategies to ensure safe updates to active financial offers without disrupting customer journeys or reward tracking.

\section{Testing and Validation}

I performed extensive testing and validation activities to ensure application stability, responsiveness, and secure workflow execution across different modules. The work included UI validation, API integration testing, responsive testing, debugging, and workflow verification with special attention to secure transaction handling and EMI-related operations. These contributions improved frontend scalability, strengthened synchronization between frontend and backend systems, and enhanced the overall reliability and modernization of the CBCC-PWA ecosystem.