\begin{tikzpicture}[remember picture, overlay]
	\draw[line width = 4pt] ($(current page.north west) + (0.75in,-0.75in)$) rectangle ($(current page.south east) + (-0.75in,0.75in)$);
\end{tikzpicture}
\thispagestyle{empty}
\begin{center}
	%.\hspace{1cm}\\ \par
	\Large\textbf{\underline{ACKNOWLEDGEMENTS}} \par
\end{center}

I express my sincere gratitude to \textbf{Dr. Ramakanth Kumar P}, Professor and Dean (CSE Cluster), RV College of Engineering, for his visionary leadership, constant encouragement, and for fostering an environment that supports industry-academic engagement through internship opportunities.

I am deeply thankful to \textbf{Dr. Shanta Rangaswamy}, Professor and Head, Department of Computer Science and Engineering, RVCE, for her constant support, guidance, and for facilitating the smooth conduct of the internship program within the department.

I am sincerely indebted to my guide, \textbf{Prof. Dr. H K Krishnappa}, Professor, Department of Computer Science and Engineering, RV College of Engineering, for his wholehearted support, invaluable suggestions, and expert advice throughout my internship work. His thorough review of my report, constructive feedback, and continued guidance have been the cornerstone of this work.

I wish to express my sincere gratitude to \textbf{Shristi Singh}, Product Manager,  for providing me with the opportunity to intern at their esteemed organization. I am grateful for their valuable guidance, professional mentorship, and for providing the necessary resources to complete my internship successfully.

I sincerely thank \textbf{Dr. Chethana R Murthy}, Assistant Professor, Department of CSE, RVCE, for patiently helping me resolve all queries regarding the report, important submission dates, and for her guidance in relation to the major project. Her timely assistance was invaluable throughout the internship.

I extend my heartfelt thanks to \textbf{Ms. Deepika Dash}, Assistant Professor, Department of CSE, RVCE, for her dedicated support in the preparation and structuring of this internship report and for guiding me at every step of the documentation process.

I express my sincere gratitude to our beloved Vice Principal, \textbf{Dr. Geetha K S}, and Principal, \textbf{Dr. K. N. Subramanya}, RVCE, for their leadership and encouragement toward such practical learning experiences.

Finally, I thank all the teaching and technical staff of the Department of Computer Science and Engineering, as well as my family and friends, for their constant support throughout the duration of this internship.