\chapter{Reflections}

\section{Results}

The internship contributed significantly to the enhancement and modernization of the CBCC-PWA platform through improvements in frontend architecture, secure API integration, and workflow optimization. The implemented solutions improved application responsiveness, strengthened authentication handling, and enabled the development of reusable and scalable frontend components across multiple modules. A major achievement was the contribution to the Live Offer Versioning Workflow, which supported safe production updates for financial offers while minimizing operational risks and ensuring uninterrupted customer experiences.

\section{Learning Outcomes}

During the internship, I gained practical experience in modern frontend technologies including React, Redux, TypeScript, REST API integration, and Progressive Web Application (PWA) architecture. I also developed a deeper understanding of secure authentication workflows, enterprise-level frontend design systems, and the challenges involved in building scalable financial applications used in real-world environments. In addition to technical skills, the internship strengthened my professional communication, teamwork, problem-solving, and time management abilities while working in a collaborative corporate setting. It also provided exposure to agile development practices, technical documentation standards, and the importance of writing maintainable and scalable software solutions.

\section{Conclusion}

The internship provided valuable industry exposure and helped bridge the gap between academic learning and practical software engineering experience. Working on the CBCC-PWA platform allowed me to apply theoretical concepts to real-world financial technology solutions while improving both my technical expertise and professional skills. Overall, the experience enhanced my understanding of enterprise application development and prepared me for future opportunities in software development and fintech domains.